### 2016-02-17 doc/toy.tex
add multiple photometric points and covariance. Implement "N choose k" selection criteria.  Runs and OK-looking results on laptop

\subsection{Case Typed}
For Case Typed the likelihood is
\begin{align}
\mathcal{L}(T_o,z_o,c_o | S_c, S_T, z, X) & =  \int dL \sum_i p(T_o,z_o,c_o | T_i, L, S_c, S_T, z, X) p(L |  T_i,  S_c, S_T, z, X) P(T_i|S_c, S_T, z, X).
\end{align}
We assume that the observations give a perfect measurement of type and redshift,
so that
\begin{align}
p(T_o|T) & =\delta(T_o-T)\\
p(z_o|z) & =\delta(z_o-z);
\end{align}
practically $T$ and $z$ are no longer probabilistic but are fixed.
Then
\begin{align}
\mathcal{L}(T_o,z_o,c_o | S_c, S_T, z, X) & =  \int dL p(c_o | T=T_o, L, S_c, S_T, z=z_o, X) p(L| T=T_o, S_c, S_T, z=z_o, X)  P(T_o|S_c, S_T, z=z_o, X) \\
&= \int dL \frac{ p(c_o, S_c, S_T | T=T_o, L, z=z_o, X) }{P(S_c, S_T, | T=T_o, L,  z=z_o, X) }
\frac{p(L, S_c, S_T | T=T_o, z=z_o, X)}{P(S_c, S_T| T=T_o,  z=z_o, X)}
\frac{p(T_o, S_c, S_T | z=z_o, X)}{P(S_c, S_T| z=z_o, X)} \\
&= \frac{\int dL p(L|T_o, z=z_o, X) P(T_o|z=z_o, X) p(c_o, S_c, S_T | T=T_o, L, z=z_o, X)}{P(S_c, S_T| z=z_o, X)}
\end{align}

The normalization term is determined by
\begin{align}
P(S_c, S_T| z=z_o, X) & =\sum_i \int_{-\infty}^{\infty} dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X) \\
& = \sum_i \int_{c_T}^{\infty} dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X)\\
& = \sum_i  P(T_i|z=z_o, X)\int dL p(L|T_i, z=z_o, X)  \left[\int_{c_T}^{\infty} dc_o  p(c_o | T=T_i, L, z=z_o, X)\right]
\end{align}
as $p(c_o | T=T_o, L, z)=0$ when $c_o < c_T$.

@@

For the redshift measurement, we take a set of potential host galaxies, where galaxy $j$
are redshift $z_j$ has probability $p_j$ of being the host
\begin{equation}
p(z_o|S_c, S_T, z, X) = \sum_j p_j\delta(z_j-z).
\end{equation}
Then
\begin{align}
\mathcal{L}(z_o,c_o | S_c, z, X) & =  \sum_j p_j \int dL \sum_{i} p(c_o | T_i, L, S_c, z=z_j, X) p(L |  T_i,  S_c,  z=z_j, X) P(T_i|S_c, z=z_j, X) \\
&=  \frac{\sum_j p_j \int dL p(c_o, S_c | L, z=z_j, X) \sum_{i}  p(L|T_i, z=z_j, X) P(T_i|z=z_j, X)   }{P(S_c| z=z_j, X)},
\end{align}
where we use the fact that the counts do not directly depend on type.

The normalization term is
\begin{align}
P(S_c| z=z_o, X) & = \int_{c_T}^{\infty} dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X)\\
& =  \sum_j p_j  \sum_{i} P(T_i|z=z_j, X)  \int dL  p(L|T_i, z=z_j, X) 
\left[ \int_{c_T}^\infty dc_o p(c_o| T=T_i, L, z=z_j, X) \right].
\end{align}

>>>>

\subsection{Case Typed}
For Case Typed the likelihood is
\begin{align}
\mathcal{L}(T_o,z_o,c_o | S_c, S_T, z, X) & =  \int dL \sum_i p(T_o,z_o,c_o | T_i, L, S_c, S_T, z, X) p(L |  T_i,  S_c, S_T, z, X) P(T_i|S_c, S_T, z, X).
\end{align}
We assume that the observations give a perfect measurement of type and redshift,
so that
\begin{align}
p(T_o|T) & =\delta(T_o-T)\\
p(z_o|z) & =\delta(z_o-z);
\end{align}
practically $T$ and $z$ are no longer probabilistic but are fixed.
Then
\begin{align}
\mathcal{L}(T_o,z_o,c_o | S_c, S_T, z, X) & =  \int dL\, p(c_o | T=T_o, L, S_c, S_T, z=z_o, X) p(L| T=T_o, S_c, S_T, z=z_o, X)  P(T_o|S_c, S_T, z=z_o, X) \\
&= \int dL\, \frac{ p(c_o, S_c, S_T | T=T_o, L, z=z_o, X) }{P(S_c, S_T, | T=T_o, L,  z=z_o, X) }
\frac{p(L, S_c, S_T | T=T_o, z=z_o, X)}{P(S_c, S_T| T=T_o,  z=z_o, X)}
\frac{p(T_o, S_c, S_T | z=z_o, X)}{P(S_c, S_T| z=z_o, X)} \\
&= \frac{\int dL\, p(L|T_o, z=z_o, X) P(T_o|z=z_o, X) p(c_o, S_c, S_T | T=T_o, L, z=z_o, X)}{P(S_c, S_T| z=z_o, X)}\\
&= \frac{\int dL\, p(L|T_o, z=z_o, X) P(T_o|z=z_o, X) p(c_o | T=T_o, L, z=z_o, X)}{P(S_c, S_T| z=z_o, X)}.
\end{align}

The  normalization term sums/integrates over all possible observed types/counts 
\begin{align}
P(S_c, S_T| z=z_o, X) & =\sum_i \int dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X) \\
% & =\sum_i \int_{-\infty}^{\infty} dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X) \\
%& = \sum_i \int_{c_T}^{\infty} dc_o \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X)\\
& = \sum_i  P(T_i|z=z_o, X)\int dL\, p(L|T_i, z=z_o, X)  \left[\int dc_o\,  p(c_o,S_c, S_T | T=T_i, L, z=z_o, X)\right].
\end{align}

In the case of a single count measurement per transient and neglecting the typing selection criteria,
\begin{align}
 p(c_o, S_c, S_T | T=T_o, L, z=z_o, X) &=  p(c_o, c_o \ge  c_T | T=T_o, L, z=z_o, X) \\
 &= \begin{cases}
   p(c_o | T=T_o, L, z=z_o, X) & \text{if } c_o \ge c_T \\
   0 & \text{if }  c_o < c_T
 \end{cases}
\end{align}
so that the integral in brackets is
\begin{equation}
\int dc_o \, p(c_o,S_c, S_T | T=T_i, L, z=z_o, X) = \int_{c_T}^\infty dc_o\,  p(c_o | T=T_i, L, z=z_o, X).
\end{equation}

For the more general case, suppose a transient has $N$ independent count measurements\footnote{The independence of count measurements  depends on the flux extraction method; regardless the
noise of a single observation is expected to be dominated by its own photon noise making this
supposition a good approximation.} and $k$ of those must be above threshold in order to be
included in the sample.
Consider arrays of length $N$ in which each element has a value of True or False: there are $2^N$ possible configurations for this array
of which $\sum_{i=k}^N {N \choose i}$ have $k$ or more True's.  Let the set $\mathcal{G}$ represent the latter possible configurations.
Then
\begin{align}
p(c_o, S_c| T=T_o, L, z=z_o, X) &= \sum_{g \in \mathcal{G}} \prod_{\alpha} p(c_{o, \alpha}, g | T=T_o, L, z=z_o, X)\\
 &=  \sum_{g \in \mathcal{G}}  \prod_{\alpha} \begin{cases}
   p(c_{o,\alpha} | T=T_o, L, z=z_o, X) & \text{if } c_{o,\alpha} \ge c_T == g_\alpha \\
   0 & \text{if }  c_{o,\alpha} \ge c_T\  != g_\alpha
 \end{cases}
\end{align}
and the normalization integral is composed of the sum over all possible configurations of the integrated probability of the truncated distributions
of the measured counts.  This simplifies to the the single-count case considered earlier in the case of $N=1$, $k=1$.

@@

For the redshift measurement, we take a set of potential host galaxies, where galaxy $j$
are redshift $z_j$ has probability $p_j$ of being the host
\begin{equation}
p(z_o|S_c, S_T, z, X) = \sum_j p_j\delta(z_j-z).
\end{equation}
Then
\begin{align}
\mathcal{L}(z_o,c_o | S_c, z, X) & =  \sum_j p_j \int dL \,\sum_{i} p(c_o | T_i, L, S_c, z=z_j, X) p(L |  T_i,  S_c,  z=z_j, X) P(T_i|S_c, z=z_j, X) \\
&=  \frac{\sum_j p_j \int dL \, p(c_o, S_c | L, z=z_j, X) \sum_{i}  p(L|T_i, z=z_j, X) P(T_i|z=z_j, X)   }{P(S_c| z=z_j, X)}\\
&=  \frac{\sum_j p_j \int dL \, p(c_o | L, z=z_j, X) \sum_{i}  p(L|T_i, z=z_j, X) P(T_i|z=z_j, X)   }{P(S_c| z=z_j, X)},
\end{align}
where we use the fact that the counts do not directly depend on type.

The normalization term is
\begin{align}
P(S_c| z=z_o, X) & = \int dc_o \, \mathcal{L}(T_i,z_o,c_o | S_c, S_T, z, X)\\
& =  \sum_j p_j  \sum_{i} P(T_i|z=z_j, X)  \int dL \, p(L|T_i, z=z_j, X) 
\left[ \int dc_o \, p(c_o, S_c| T=T_i, L, z=z_j, X) \right].
\end{align}
